The Talking Heads Experiment

### 2015-04-10 chap11/chap11.tex
cumulative update, mainly for Ch. 7-12

This chapter discusses additional language game experiments directly inspired by the Talking Heads experiment, 
set up after 2005. Major breakthroughs along several dimensions have been achieved. Robots became hugely 
more complex, with humanoid shapes, and going from a few degrees of sensing and actuation to close to a hundred. The grammar 
formalisms developed for language game experiments matured, specifically the Fluid Construction Grammar formalism, developed 
as a successor of the COGAR formalism reported in the previous chapter.\footnote{
A full introduction into Fluid Construction Grammar \is{Fluid Construction Grammar} 
is beyond the scope of this book. The interested reader is 
referred to the following two paper collections: \cite{Steels:2011} and \cite{Steels:2012}.}
Semantics was scaled up from propositional and predicate logic to fully open-ended procedural semantics.
And last but not least the theory of semiotic dynamics received a major impetus when statistical physicists became seriously 
involved, applying techniques and methods from complex systems science to study language game
dynamics, \cite{Loreto:2007}. \is{semiotic dynamics}
A large number of contributions were made by Loreto's Statistical Physics group at the University of Rome (La Sapienza), 
see in particular: \cite{DallaAsta:2006} and \cite{Baronchelli:2012}.
A full overview of all these developments is beyond the 
scope of this book. Instead we only look here at developments that directly pertain to language game experiments with robots.

@@

Around 2005, the same team that had built the AIBO robot at the Sony Corporation central laboratories, managed to 
make another enormous leap forward by building \is{Proper Naming Game}
the QRIO humanoid robot. This robot is about 60 cm tall and weighs 7.3 kg. Its sensors
include two cameras in the head, a microphone, and sensors in each motor joint to monitor posture and movement. The robot has enough
computing power and battery to autonomously walk around on its two legs and perform various actions in the world.
The QRIO never made it to a commercial product for economical reasons. However, we were able to use QRIO robots to 
carry out a series of ground-breaking experiments that without doubt pushed the state of the art in language games
forward considerably. 
The teleportation infrastructure developed for the original Talking Heads experiment was used again 
to allow experiments with populations of agents, despite having only a few robotic bodies available. 
For every game, two agents were downloaded into the on-board memory and processors 
of the QRIO robot and after a game, the state of the agent was uploaded back to a central server. Agents never
interacted without being physically instantiated in the world.

@@

In January 2007, Luc Steels, Martin Loetzsch, and Michael Spranger traveled to the Sony Computer Science Laboratory 
in Tokyo to do the first experiments with the QRIO robots.  
We decided to redo the Talking Heads experiment, but focusing on proper names for individual objects, rather than the emergence 
of generic terms such as colours, shapes or positions.\footnote{The first paper on the Proper Naming Game is: \cite{Steels:2007}
It also discusses the concept of a semiotic network. 
A more recent paper is: \cite{Steels:2012b}. A more 
in-depth discussion of the experiment is included 
in the Ph.D thesis of Martin Loetzsch, defended in 2014 at Humboldt University.}

@@

The general set-up for the Proper Naming Game experiment
is shown in \figref{fig:grounded}. We see two QRIO robots and an environment consisting of objects of various 
sizes and shapes. At any time a new object can be added or the position of an object can be changed. So the world is 
entirely open and robots do not know how many individuals there are. 
Importantly, the robots had to recognise an object as an individual, independently of its position. If 
a specific object disappeared from the world and was put back later, the same name would still have to be used. \\

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.80\textwidth]{chap11/figs/grounded-naming-game.pdf}}
\caption{\label{fig:grounded} 
Set-up for the Grounded Proper Naming Game. Two Qrio robots are playing a game of reference about individual objects 
in their environment. They are using proper names and hence have to recognise objects as individuals.}
\end{figure}

{\bfshape Challenges} \\

It is useful to emphasise how extraordinary difficult this task is, even though the Talking Heads experiment and 
earlier experiments with the AIBO already 
provided a good foundation. These difficulties are encountered for communication within any group of
autonomous physically embodied agents and hence also humans. 
First of all it is extremely challenging to set up joint-attention frames with free roaming
robots, which may explain why no other animals except humans can self-organise
shared symbolic systems. For the Proper Naming Game experiment, a robot moves around until another robot comes into 
view and remains sufficiently 
stationary. Both robots follow this strategy and so sooner or later a pair of robots find each other
and a game becomes possible. Next the robots both scan their immediate environment and build up an initial world model. 
They keep tracking the environment because it may change as games are being played. 
Because the robots can detect each other, they can reconstruct what the scene looks like from the other's point of 
view, which is particularly relevant for experiments on spatial language discussed later. 
Moreover the speaker could provide a correction in case of 
communicative failure by physically pointing to the topic, although the resolution of the vision system of the QRIO was not 
fine-grained enough to actually detect pointing gestures, so the direction of pointing was transmitted directly, although
this is still a noisy communication channel because the observer has to interpret this direction in terms of his own 
perception of what the other agent might be seeing.

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.85\textwidth]{chap10/figs/png-perception.pdf}}
\caption{\label{fig:png-perception} 
A robot is looking at consecutive scenes (from top to bottom) and tracking the objects in the scene. One object (labeled $O_{716}$)
is moved by a human experimenter.  We see from left to right: the original source image, results of region detection and 
colour segmentation, the (average) value for one dimension of one object ($O_{716}$), the segmented and labeled objects, 
and the world model, including the position of the other robot (indicated by a pointing arrow). }
\end{figure}

@@

{\bfshape Semiotic networks}\\

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.95\textwidth]{chap10/figs/prototypes-identifiers-words.pdf}}
\caption{\label{fig:prototypes-identifiers-words} 
In the Proper Naming Game experiment the memory of the agents is conceived in terms of a semiotic network that 
spans the full semiotic cycle from sensory experience and conceptualisation to naming.}
\end{figure}

@@

We have operationalised just one example of such a heuristic. When an object is moving or being moved,
its appearance may change but the observer tracking the object 
still knows that he is dealing with the same object and so he can
exploit this information to fine-tune his semiotic networks. Because the vision system we used on the QRIO robots, developed 
by Michael Spranger,\footnote{
This system is described in-depth in: \cite{Spranger:2012vision}.} is able to track an object, it can align object
regions across different images, enriched with top-down predictions of
how an object region will change over time based on Recursive Bayesian
estimation using Kalman filters. The object being moved by 
the experimenter in \figref{fig:png-perception} 
yields two quite different sensory experiences when standing up or lying down which match with 
two different prototypes, but thanks to the tracking heuristic, the semiotic network can 
be rearranged to reflect that they are two views of the same object (see \figref{fig:png-optimisation}).

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.75\textwidth]{chap11/figs/adjust-id.pdf}}
\caption{\label{fig:png-optimisation} 
When the identity of two objects is discovered (because two prototypical views have been established 
as belonging to the same individual object), the former nodes for identities can be merged while keeping the 
links to their names intact. 
}
\end{figure}

@@

As a second example of how thinking in terms of semiotic networks is useful,
we turn to an experiment building further on the work on action-word learning \is{action game}
using the AIBO reported in the previous chapter.
It was first designed and carried out with the QRIO robot in 2007/2008 by Luc Steels and
Michael Spranger with considerable help from Martin Loetzsch\footnote{Papers describing this experiment more fully are: 
\cite{Steels:2008spatial} and \cite{Steels:2008b}.} and 
then ported in 2010 to the MYON, a robot developed by Manfred Hild and his team at the Humboldt 
University in Berlin (see \figref{fig:myon-action}) (\cite{Steels:2012b}). 
A BBC video clip of the experiment can be seen here: \\
https://www.youtube.com/watch?v=lmoXByLkK14
The porting exercise showed that once we discover how to do a certain type of language game on one robot 
we can relatively easily transfer it to another one, after adapting the lowest level sensing and actuation routines.

@@

\begin{figure}
\centerline{\includegraphics[width=0.2\linewidth]{chap11/figs/postures.pdf}\includegraphics[width=0.75\linewidth]{chap11/figs/vision_2.pdf}}
\caption{\label{vision} \footnotesize{{\itshape Left:} Example postures of the robot (which is the QRIO in this case).
{\itshape Right:} Visual analysis. From left to right we see the source image, the foreground/background distinction and object segmentation (focusing on the upper torso), and the feature signature of this posture represented as a graph connecting the values (on the y-axis)
of the seven centralised normalised moments (on the x-axis).}}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=0.6\linewidth]{chap11/figs/robot-mirror.pdf}}
\caption{\label{robot-mirror} \footnotesize{The QRIO humanoid robot stands before a mirror and performs various motor behaviours thus observing what visual body-images these behaviours generate.}}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=0.6\linewidth]{chap11/figs/commsuccess.pdf}}
\caption{\label{commsuccess} \footnotesize{Results of the Action Game played by a population of 10 agents 
for 10 postures after coordinating image schemata and motor control through a mirror. 
The x-axis plots the number of language games. The y-axis shows the running average of 
communicative success and average lexicon size.}}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=0.6\linewidth]{chap11/figs/network.pdf}}
\caption{ \label{network} Semiotic network linking sensory experiences, visual prototypes of postures, nodes for postures acting as mirror neurons, and nodes triggering the motor behaviour that achieves the posture. Nodes for words (shown as squares) 
are associated with the posture nodes.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.65\textwidth]{chap11/figs/color-qrio.pdf}}
\caption{\label{fig:munsell} 
Set-up with two QRIO humanoids, similar to Munsell chip tests used in psychology. The same game as the Talking 
Heads was used, but only colour chips were provided as input and the robots use pointing and head movements to 
provide feedback.}
\end{figure}

When the QRIO humanoid robots became available, we decided to use this existing work for pushing forward the state of 
the art in colour language research in two ways:
\begin{itemize}
\item To use more realistic circumstances of object perception. Because 
robots are moving around in three dimensions and see the situation from different points of view, the reflection 
of light changes and is different for speaker and hearer (see \tabref{f:scene-example}). This difference did not 
play a role in earlier experiments but 
it certainly plays an important role in the stabilisation and choice of colour prototypes. 
\item To focus on colour descriptions beyond basic colour terms, i.e. descriptions like 
`slightly blue', `blue-green', `bluish green', `very bright', `shiny yellow', `dark red', `sky blue', 
`very dark bluish red', etc. Indeed, it turns out that 
basic colour terms are used only in about 10 to 15 \% of the occurrences of colour descriptions. The rest are 
more complex expressions. Complex colour descriptions require scaling up the semantics and introducing grammar, they 
also require the introduction of language strategies as a layer of abstraction 
above lexical and grammatical constructions. 
\end{itemize}

@@

{\bfshape Compositional Procedural Semantics with IRL}\\

@@

{\bfshape Building Blocks for Natural Language Semantics }\\

@@

{\bfshape Strategies for Colour} \\

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=1.0\textwidth]{chap11/figs/basic-strat.pdf}}
\caption{\label{fig:basic-strat} 
Constraint network for the Basic Colour strategy. The colours of each object in the context are retrieved, their 
similarity to the prototype computed, and the one with the highest similarity is chosen.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=1.0\textwidth]{chap11/figs/graded.pdf}}
\caption{\label{fig:graded} 
Constraint network implementing the Graded Membership Strategy. It builds further on the network for Basic Colour
Categorisation but adds a constraint to handle graded membership. }
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=1.0\textwidth]{chap11/figs/combi.pdf}}
\caption{\label{fig:combi} 
Constraint network implementing the Colour Combination strategy leading to expressions like `greenish blue'. 
The filter-by-colour operation now has an extra argument, namely category-sets,  
and there is a draw-category-set-to-category operation that rescales the basic colour category set.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=1.0\textwidth]{chap11/figs/modi.pdf}}
\caption{\label{fig:modi} 
Constraint network for the basic modification strategy, for expressions like `light green'.}
\end{figure}

@@

{\bfshape Translation to Grammar} \\

@@

{\bfshape Influence of embodiment}\\

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=0.6\textwidth]{chap11/figs/grounding-comparison.pdf}}
\caption{ Comparison of three different environmental set-ups (left, right, and middle columns)
and four different learning conditions. Communicative success is shown on the y-axis.}
\label{fig:grounding-comparison} 
\end{figure}

>>>>

This chapter discusses additional language game experiments directly inspired by the Talking Heads experiment, 
set up after 2005. Major breakthroughs along several dimensions have been achieved. Robots became hugely 
more complex, with humanoid shapes, and going from a few degrees of sensing and actuation to close to a hundred. The grammar 
formalisms developed for language game experiments matured, specifically the Fluid Construction Grammar formalism, developed 
as a successor of the \textsc{cogar} formalism reported in the previous chapter.\footnote{
A full introduction into Fluid Construction Grammar \is{Fluid Construction Grammar} 
is beyond the scope of this book. The interested reader is 
referred to the following two paper collections: \cite{Steels:2011} and \cite{Steels:2012}.}
Semantics was scaled up from propositional and predicate logic to fully open-ended procedural semantics.
And last but not least the theory of semiotic dynamics received a major impetus when statistical physicists became seriously 
involved, applying techniques and methods from complex systems science to study language game
dynamics, \cite{Loreto:2007}. \is{semiotic dynamics}
A large number of contributions were made by Loreto's Statistical Physics group at the University of Rome (La Sapienza), 
see in particular: \cite{DallaAsta:2006} and \cite{Baronchelli:2012}.
A full overview of all these developments is beyond the 
scope of this book. Instead we only look here at developments that directly pertain to language game experiments with robots.

@@

Around 2005, the same team that had built the \textsc{aibo} robot at the Sony Corporation central laboratories, managed to 
make another enormous leap forward by building \is{Proper Naming Game}
the \textsc{qrio} humanoid robot. This robot is about 60 cm tall and weighs 7.3 kg. Its sensors
include two cameras in the head, a microphone, and sensors in each motor joint to monitor posture and movement. The robot has enough
computing power and battery to autonomously walk around on its two legs and perform various actions in the world.
The \textsc{qrio} never made it to a commercial product for economical reasons. However, we were able to use \textsc{qrio} robots to 
carry out a series of ground-breaking experiments that without doubt pushed the state of the art in language games
forward considerably. 
The teleportation infrastructure developed for the original Talking Heads experiment was used again 
to allow experiments with populations of agents, despite having only a few robotic bodies available. 
For every game, two agents were downloaded into the on-board memory and processors 
of the \textsc{qrio} robot and after a game, the state of the agent was uploaded back to a central server. Agents never
interacted without being physically instantiated in the world.

@@

In January 2007, Luc Steels, Martin Loetzsch, and Michael Spranger traveled to the Sony Computer Science Laboratory 
in Tokyo to do the first experiments with the \textsc{qrio} robots.  
We decided to redo the Talking Heads experiment, but focusing on proper names for individual objects, rather than the emergence 
of generic terms such as colours, shapes or positions.\footnote{The first paper on the Proper Naming Game is: \cite{Steels:2007}
It also discusses the concept of a semiotic network. 
A more recent paper is: \cite{Steels:2012b}. A more 
in-depth discussion of the experiment is included 
in the Ph.D thesis of Martin Loetzsch, defended in 2014 at Humboldt University.}

@@

The general set-up for the Proper Naming Game experiment
is shown in \figref{fig:grounded}. We see two \textsc{qrio} robots and an environment consisting of objects of various 
sizes and shapes. At any time a new object can be added or the position of an object can be changed. So the world is 
entirely open and robots do not know how many individuals there are. 
Importantly, the robots had to recognise an object as an individual, independently of its position. If 
a specific object disappeared from the world and was put back later, the same name would still have to be used. \\

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.80\textwidth]{chap11/figs/grounded-naming-game.pdf}}
\caption{\label{fig:grounded}Set-up for the Grounded Proper Naming Game. Two Qrio robots are playing a game of reference about individual objects 
in their environment. They are using proper names and hence have to recognise objects as individuals.}
\end{figure}

\subsection{Challenges}
% {\bfshape Challenges} \\

It is useful to emphasise how extraordinary difficult this task is, even though the Talking Heads experiment and 
earlier experiments with the \textsc{aibo} already 
provided a good foundation. These difficulties are encountered for communication within any group of
autonomous physically embodied agents and hence also humans. 
First of all it is extremely challenging to set up joint-attention frames with free roaming
robots, which may explain why no other animals except humans can self-organise
shared symbolic systems. For the Proper Naming Game experiment, a robot moves around until another robot comes into 
view and remains sufficiently 
stationary. Both robots follow this strategy and so sooner or later a pair of robots find each other
and a game becomes possible. Next the robots both scan their immediate environment and build up an initial world model. 
They keep tracking the environment because it may change as games are being played. 
Because the robots can detect each other, they can reconstruct what the scene looks like from the other's point of 
view, which is particularly relevant for experiments on spatial language discussed later. 
Moreover the speaker could provide a correction in case of 
communicative failure by physically pointing to the topic, although the resolution of the vision system of the \textsc{qrio} was not 
fine-grained enough to actually detect pointing gestures, so the direction of pointing was transmitted directly, although
this is still a noisy communication channel because the observer has to interpret this direction in terms of his own 
perception of what the other agent might be seeing.

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.85\textwidth]{chap10/figs/png-perception.pdf}}
\caption{\label{fig:png-perception}A robot is looking at consecutive scenes (from top to bottom) and tracking the objects in the scene. One object (labeled $O_{716}$)
is moved by a human experimenter.  We see from left to right: the original source image, results of region detection and 
colour segmentation, the (average) value for one dimension of one object ($O_{716}$), the segmented and labeled objects, 
and the world model, including the position of the other robot (indicated by a pointing arrow). }
\end{figure}

@@

\subsection{Semiotic networks}\todo{This used to be set in a \textbackslash bfshape and not in a subsection}
% {\bfshape Semiotic networks}\\

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.95\textwidth]{chap10/figs/prototypes-identifiers-words.pdf}}
\caption{\label{fig:prototypes-identifiers-words}In the Proper Naming Game experiment the memory of the agents is conceived in terms of a semiotic network that 
spans the full semiotic cycle from sensory experience and conceptualisation to naming.}
\end{figure}

@@

We have operationalised just one example of such a heuristic. When an object is moving or being moved,
its appearance may change but the observer tracking the object 
still knows that he is dealing with the same object and so he can
exploit this information to fine-tune his semiotic networks. Because the vision system we used on the \textsc{qrio} robots, developed 
by Michael Spranger,\footnote{
This system is described in-depth in: \cite{Spranger:2012vision}.} is able to track an object, it can align object
regions across different images, enriched with top-down predictions of
how an object region will change over time based on Recursive Bayesian
estimation using Kalman filters. The object being moved by 
the experimenter in \figref{fig:png-perception} 
yields two quite different sensory experiences when standing up or lying down which match with 
two different prototypes, but thanks to the tracking heuristic, the semiotic network can 
be rearranged to reflect that they are two views of the same object (see \figref{fig:png-optimisation}).

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.75\textwidth]{chap11/figs/adjust-id.pdf}}
\caption{\label{fig:png-optimisation}When the identity of two objects is discovered (because two prototypical views have been established 
as belonging to the same individual object), the former nodes for identities can be merged while keeping the 
links to their names intact. 
}
\end{figure}

@@

As a second example of how thinking in terms of semiotic networks is useful,
we turn to an experiment building further on the work on action-word learning \is{action game}
using the \textsc{aibo} reported in the previous chapter.
It was first designed and carried out with the \textsc{qrio} robot in 2007/2008 by Luc Steels and
Michael Spranger with considerable help from Martin Loetzsch\footnote{Papers describing this experiment more fully are: 
\cite{Steels:2008spatial} and \cite{Steels:2008b}.} and 
then ported in 2010 to the MYON, a robot developed by Manfred Hild and his team at the Humboldt 
University in Berlin (see \figref{fig:myon-action}) (\cite{Steels:2012b}). 
A BBC video clip of the experiment can be seen here: \\
https://www.youtube.com/watch?v=lmoXByLkK14
The porting exercise showed that once we discover how to do a certain type of language game on one robot 
we can relatively easily transfer it to another one, after adapting the lowest level sensing and actuation routines.

@@

\begin{figure}
\centerline{\includegraphics[width=0.2\linewidth]{chap11/figs/postures.pdf}\includegraphics[width=0.75\linewidth]{chap11/figs/vision_2.pdf}}
\caption{\label{vision}{\itshape Left:} Example postures of the robot (which is the \textsc{qrio} in this case).
{\itshape Right:} Visual analysis. From left to right we see the source image, the foreground/background distinction and object segmentation (focusing on the upper torso), and the feature signature of this posture represented as a graph connecting the values (on the y-axis)
of the seven centralised normalised moments (on the x-axis).}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=0.6\linewidth]{chap11/figs/robot-mirror.pdf}}
\caption{\label{robot-mirror}The \textsc{qrio} humanoid robot stands before a mirror and performs various motor behaviours thus observing what visual body-images these behaviours generate.}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=0.6\linewidth]{chap11/figs/commsuccess.pdf}}
\caption{\label{commsuccess}Results of the Action Game played by a population of 10 agents 
for 10 postures after coordinating image schemata and motor control through a mirror. 
The x-axis plots the number of language games. The y-axis shows the running average of 
communicative success and average lexicon size.}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=0.6\linewidth]{chap11/figs/network.pdf}}
\caption{\label{network} Semiotic network linking sensory experiences, visual prototypes of postures, nodes for postures acting as mirror neurons, and nodes triggering the motor behaviour that achieves the posture. Nodes for words (shown as squares) 
are associated with the posture nodes.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.65\textwidth]{chap11/figs/color-qrio.pdf}}
\caption{\label{fig:munsell}Set-up with two \textsc{qrio} humanoids, similar to Munsell chip tests used in psychology. The same game as the Talking 
Heads was used, but only colour chips were provided as input and the robots use pointing and head movements to 
provide feedback.}
\end{figure}

When the \textsc{qrio} humanoid robots became available, we decided to use this existing work for pushing forward the state of 
the art in colour language research in two ways:
\begin{itemize}
\item To use more realistic circumstances of object perception. Because 
robots are moving around in three dimensions and see the situation from different points of view, the reflection 
of light changes and is different for speaker and hearer (see \tabref{f:scene-example}). This difference did not 
play a role in earlier experiments but 
it certainly plays an important role in the stabilisation and choice of colour prototypes. 
\item To focus on colour descriptions beyond basic colour terms, i.e. descriptions like 
`slightly blue', `blue-green', `bluish green', `very bright', `shiny yellow', `dark red', `sky blue', 
`very dark bluish red', etc. Indeed, it turns out that 
basic colour terms are used only in about 10 to 15 \% of the occurrences of colour descriptions. The rest are 
more complex expressions. Complex colour descriptions require scaling up the semantics and introducing grammar, they 
also require the introduction of language strategies as a layer of abstraction 
above lexical and grammatical constructions. 
\end{itemize}

@@

\subsection{Compositional Procedural Semantics with IRL}
% {\bfshape Compositional Procedural Semantics with IRL}\\

@@

\subsection{Building Blocks for Natural Language Semantics}
% {\bfshape Building Blocks for Natural Language Semantics }\\

@@

\subsection{Strategies for colour}
% {\bfshape Strategies for Colour} \\

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=1.0\textwidth]{chap11/figs/basic-strat.pdf}}
\caption{\label{fig:basic-strat}Constraint network for the Basic Colour strategy. The colours of each object in the context are retrieved, their 
similarity to the prototype computed, and the one with the highest similarity is chosen.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=1.0\textwidth]{chap11/figs/graded.pdf}}
\caption{\label{fig:graded}Constraint network implementing the Graded Membership Strategy. It builds further on the network for Basic Colour
Categorisation but adds a constraint to handle graded membership. }
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=1.0\textwidth]{chap11/figs/combi.pdf}}
\caption{\label{fig:combi}Constraint network implementing the Colour Combination strategy leading to expressions like `greenish blue'. 
The filter-by-colour operation now has an extra argument, namely category-sets,  
and there is a draw-category-set-to-category operation that rescales the basic colour category set.}
\end{figure}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=1.0\textwidth]{chap11/figs/modi.pdf}}
\caption{\label{fig:modi}Constraint network for the basic modification strategy, for expressions like `light green'.}
\end{figure}

@@

\subsection{Translation to grammar}
% {\bfshape Translation to Grammar} \\

@@

\subsection{Influence of embodiment}
% {\bfshape Influence of embodiment}\\

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=\textwidth]{chap11/figs/grounding-comparison.pdf}}
\caption{Comparison of three different environmental set-ups (left, right, and middle columns)
and four different learning conditions. Communicative success is shown on the y-axis.}
\label{fig:grounding-comparison} 
\end{figure}
